Analysis of pudding following Davidson 1970

### 2023-10-31 inst/carcinoma.Rmd
consistentification

---
title: "Carcinoma"
output: bookdown::html_document2
---

@@

(takes maybe twenty minutes to run without cache.  The value of
`carcinoma_maxp` is calculated separately [discussed below], and that
takes a few days to run).

<p style="text-align: right;">
![](`r system.file("help/figures/hyper2.png", package = "hyper2")`){width=10%}
</p>

>>>>

---
title: "Analysing a carcinoma dataset with the hyper2 package"
author: "R. K. S. Hankin"
output: bookdown::html_document2
bibliography: jss_hyper3.bib
---

@@

```{r out.width='20%', out.extra='style="float:right; padding:10px"',echo=FALSE}
knitr::include_graphics(system.file("help/figures/hyper2.png", package = "hyper2"))
```

To cite the `hyper2` package in publications, please use @hankin2017a
(takes maybe twenty minutes to run without cache.  The value of
`carcinoma_maxp` is calculated separately [discussed below], and that
takes a few days to run).

### 2023-10-31 inst/collusion3.Rmd
consistentification

---
title: "Chess collusion with hyper3 objects"
author: "Robin KS Hankin"
output: html_document
---

@@

<p style="text-align: right;">
![](`r system.file("help/figures/hyper2.png", package = "hyper2")`){width=10%}
</p>

We analyse results from Curacao 1962 using `hyper3` formalism using
the weighted Draw monster approach outlined in `kka.Rmd`:

>>>>

---
title: "Chess collusion with hyper3 objects"
author: "R. K. S. Hankin"
output: bookdown::html_document2
bibliography: jss_hyper3.bib
---

@@

```{r out.width='20%', out.extra='style="float:right; padding:10px"',echo=FALSE}
knitr::include_graphics(system.file("help/figures/hyper2.png", package = "hyper2"))
```

To cite the `hyper2` package in publications, please use @hankin2017a.
Here I analyse results from Curacao 1962 using `hyper3` formalism
using the weighted Draw monster approach outlined in `kka.Rmd`:

### 2023-10-31 inst/cook.Rmd
consistentification

---
title: "Domestic cooking and likelihood"
output: html_document
---

@@

<p style="text-align: right;">
![](`r system.file("help/figures/hyper2.png", package = "hyper2")`){width=10%}
</p>

Suppose there are five people in a family.  Each day for five days,
one person cooks a meal.  After the fifth day, each person considers
the four meals cooked by other family members, and puts them in order
of preference.  This very short vignette shows how to apply
generalized Bradley-Terry to this situation using the `hyper2`
package.

>>>>

---
title: "Domestic cooking and likelihood"
author: "R. K. S. Hankin"
output: bookdown::html_document2
bibliography: jss_hyper3.bib

---

@@

```{r out.width='20%', out.extra='style="float:right; padding:10px"',echo=FALSE}
knitr::include_graphics(system.file("help/figures/hyper2.png", package = "hyper2"))
```

To cite the `hyper2` package in publications, please use @hankin2017a.
Suppose there are five people in a family.  Each day for five days,
one person cooks a meal.  After the fifth day, each person considers
the four meals cooked by other family members, and puts them in order
of preference.  This very short vignette shows how to apply
generalized Bradley-Terry to this situation using the `hyper2`
package.

### 2023-10-31 inst/curling.Rmd
use sticker in Rmd
name all chunks and cache the slow ones
consistentification

---
title: "curling"
output: html_document
---

@@

[Curling](https://en.wikipedia.org/wiki/Curling) is a sport with
stones and brooms.  Following dataset taken from
[wikipedia](https://en.wikipedia.org/w/index.php?title=Curling_at_the_Winter_Olympics&oldid=998891075),
women's tournament:

@@

```{r,makehyper2curling}
curling2 <- hyper2()

@@

### References

### Package dataset

>>>>

---
title: "curling with hyper2 objects"
author: "R. K. S. Hankin"
output: bookdown::html_document2
bibliography: jss_hyper3.bib

---

@@

```{r out.width='20%', out.extra='style="float:right; padding:10px"',echo=FALSE}
knitr::include_graphics(system.file("help/figures/hyper2.png", package = "hyper2"))
```

To cite the `hyper2` package in publications, please use @hankin2017a.
[Curling](https://en.wikipedia.org/wiki/Curling) is a sport with
stones and brooms.  Following dataset taken from
[wikipedia](https://en.wikipedia.org/w/index.php?title=Curling_at_the_Winter_Olympics&oldid=998891075),
women's tournament:

@@

```{r,makehyper2curling,cache=TRUE}
curling2 <- hyper2()

@@

### Package dataset {-}

### 2023-10-31 inst/icons.Rmd
use sticker in Rmd
consistentification

---
title: "icons"
output: html_document
---

@@

This minimal document reads file `icons.txt` and creates R objects
`icons`, `icons_matrix`, and `icons_maxp`.  The dataset is discussed
extensively in West and Hankin 2008, and Hankin 2010.

>>>>

---
title: "Analysing icons for climate change and with `hyper3` objects"
author: "R. K. S. Hankin"
output: bookdown::html_document2
bibliography: jss_hyper3.bib
---

@@

```{r out.width='20%', out.extra='style="float:right; padding:10px"',echo=FALSE}
knitr::include_graphics(system.file("help/figures/hyper2.png", package = "hyper2"))
```

To cite the `hyper2` package in publications, please use @hankin2017a.
This minimal document reads file `icons.txt` and creates R objects
`icons`, `icons_matrix`, and `icons_maxp`.  The dataset is discussed
extensively in @west2008 and @hankin2010.

### 2023-10-31 inst/javelin.Rmd
statistical tests
include sticker
consistentification

---
title: "Javelins with hyper3 objects"
author: "Robin KS Hankin"
date: "10/04/2022"
output: html_document
---

@@

We analyse results from the men's javelin, 2020 Summer Olympics.

@@

Reference

>>>>

---
title: "Javelins with hyper3 objects"
author: "R. K. S. Hankin"
output: bookdown::html_document2
bibliography: jss_hyper3.bib
---

@@

```{r out.width='20%', out.extra='style="float:right; padding:10px"',echo=FALSE}
knitr::include_graphics(system.file("help/figures/hyper2.png", package = "hyper2"))
```

To cite the `hyper2` package in publications, please use @hankin2017a.
Here we analyse results from the men's javelin, 2020 Summer Olympics.

@@

```{r,dothetests,cache=TRUE}
equalp.test(javelin1)
equalp.test(javelin2)
```

### 2023-10-31 inst/jester.Rmd
consistentification

---
title: "The Jester joke recommender system"
output: html_document
---

@@

<p style="text-align: right;">
![](`r system.file("help/figures/hyper2.png", package = "hyper2")`){width=10%}
</p>

(this file creates objects `jester` and `maxjest`, which are datasets
available in the `hyper2` package, and documented at `jester.Rd`.
This file takes quite a long time to run).

Goldberg et al present a dataset in which respondents rated a number
of jokes.  Here, I analyse a small portion of this dataset using the
`hyper2` package.  This document is intended to illustrate an
extremely challenging application of the `hyper2` package and (without
cache) takes a long time to process.  Goldberg's dataset has 24938
lines, one per respondent, and 101 columns, one per joke (the first
column shows the number of jokes rated by each respondent); here I use
150 lines and 99 jokes (the 100th joke was not funny).

@@

>>>>

---
title: "The Jester joke recommender system"
author: "R. K. S. Hankin"
output: bookdown::html_document2
bibliography: jss_hyper3.bib
---

@@

```{r out.width='20%', out.extra='style="float:right; padding:10px"',echo=FALSE}
knitr::include_graphics(system.file("help/figures/hyper2.png", package = "hyper2"))
```

To cite the `hyper2` package in publications, please use @hankin2017a.
This file creates objects `jester` and `maxjest`, which are datasets
available in the `hyper2` package, and documented at `jester.Rd`.
This file takes quite a long time to run.  Goldberg et al present a
dataset in which respondents rated a number of jokes.  Here, I analyse
a small portion of this dataset using the `hyper2` package.  This
document is intended to illustrate an extremely challenging
application of the `hyper2` package and (without cache) takes a long
time to process.  Goldberg's dataset has 24938 lines, one per
respondent, and 101 columns, one per joke (the first column shows the
number of jokes rated by each respondent); here I use 150 lines and 99
jokes (the 100th joke was not funny).

@@

 ### References

### 2023-10-31 inst/loser.Rmd
consistentification

---
title: "Weakly informative observations: identifying the weakest player"
output: html_document
---

@@

<p style="text-align: right;">
![](`r system.file("help/figures/hyper2.png", package = "hyper2")`){width=10%}
</p>

# Partial rank observations: who lost?

(see also `inst/notthewinner.Rmd`).
Here we consider a situation in which we make only a rather
uninformative observation: namely, the identity of the _loser_ (which
is here taken to be me, player `a`).  We have six competitors
`a,b,c,d,e,f` with nonnegative strengths $p_1,p_2,p_3,p_4,p_5,p_6,
\sum p_i=1$.  Competitor `a` has strength $p_1$, and loses.  We are
interested in how informative this observation is with regard to
various assertions about the strength of `a`.  We have three
hypotheses:

>>>>

---
title: "Weakly informative observations: identifying the weakest player"
author: "R. K. S. Hankin"
output: bookdown::html_document2
bibliography: jss_hyper3.bib
---

@@

```{r out.width='20%', out.extra='style="float:right; padding:10px"',echo=FALSE}
knitr::include_graphics(system.file("help/figures/hyper2.png", package = "hyper2"))
```

To cite the `hyper2` package in publications, please use @hankin2017a;
see also `inst/notthewinner.Rmd`.  Here we consider a situation in
which we make only a rather uninformative observation: namely, the
identity of the _loser_ (which is here taken to be me, player `a`).
We have six competitors `a,b,c,d,e,f` with nonnegative strengths
$p_1,p_2,p_3,p_4,p_5,p_6, \sum p_i=1$.  Competitor `a` has strength
$p_1$, and loses.  We are interested in how informative this
observation is with regard to various assertions about the strength of
`a`.  We have three hypotheses:

### 2023-10-31 inst/ordertable_to_ranktable.Rmd
minor improvements
consistentification

---
title: "The print method for class ranktable"
output: html_document
---

@@

# Introduction

Rank tables can be confusing.  The package includes a range of
functionality for dealing with them, including a bespoke print method.
Here, I discuss two cases: firstly, a tiny toy example, and secondly
the volvo ocean racing dataset.

@@

```{r}
OT <- cbind(1:5,c(1,5,2:4))
rownames(OT) <- letters[seq_len(nrow(OT))]
colnames(OT) <- c("J1","J2")
OT
```

@@

```{r}
RT <- ordertable_to_ranktable(OT)
RT
```

@@

```{r}
class(RT)
class(RT) <- "matrix"  # removes "ranktable" from class list
RT
```

@@

```{r}
volvo_table
```

@@

```{r}
x <- wikitable_to_ranktable(volvo_table)
x
```

@@

```{r}
x[,1:3]
```

@@

```{r}
xx <- x[,1:3]
xx
class(xx) <- "ranktable"
xx
```

@@

```{r}
ranktable_to_printable_object(x)[,1:3]
```

>>>>

---
title: "The print method for class ranktable"
author: "R. K. S. Hankin"
output: bookdown::html_document2
bibliography: jss_hyper3.bib
---

@@

```{r out.width='20%', out.extra='style="float:right; padding:10px"',echo=FALSE}
knitr::include_graphics(system.file("help/figures/hyper2.png", package = "hyper2"))
```

To cite the `hyper2` package in publications, please use @hankin2017a.
Rank tables can be confusing.  The package includes a range of
functionality for dealing with them, including a bespoke print method.
Here, I discuss two cases: firstly, a tiny toy example, and secondly
the volvo ocean racing dataset.

@@

```{r makeatoy}
OT <- cbind(1:5,c(1,5,2:4))
rownames(OT) <- letters[seq_len(nrow(OT))]
colnames(OT) <- c("J1","J2")
OT
```

@@

```{r useordertorank}
RT <- ordertable_to_ranktable(OT)
RT
```

@@

```{r viewdirect}
class(RT)
class(RT) <- "matrix"  # removes "ranktable" from class list
RT
```

@@

```{r showvolvotable}
volvo_table
```

@@

```{r nowusewikitorank}
x <- wikitable_to_ranktable(volvo_table)
x
```

@@

```{r just3}
x[,1:3]
```

@@

```{r nowmakerank3}
xx <- x[,1:3]
xx
class(xx) <- "ranktable"
xx
```

@@

```{r showprintableobject}
ranktable_to_printable_object(x)[,1:3]
```

## References {-}

### 2023-10-31 inst/pentathlon.Rmd
consistentification

---
title: "Pentathlon"
output: bookdown::html_document2
---

@@

<p style="text-align: right;">
![](`r system.file("help/figures/hyper2.png", package = "hyper2")`){width=10%}
</p>

The [modern
pentathlon](https://en.wikipedia.org/wiki/Modern_pentathlon) is an
Olympic sport that comprises five different events: fencing, swimming,
horse riding, and running.  This short document discusses a dataset
taken from the [2004 Summer
Olympics](https://en.wikipedia.org/wiki/Modern_pentathlon_at_the_2004_Summer_Olympics),
analysing the order statistic for the top seven competitors:

>>>>

---
title: "Pentathlon"
author: "R. K. S. Hankin"
output: bookdown::html_document2
bibliography: jss_hyper3.bib
---

@@

```{r out.width='20%', out.extra='style="float:right; padding:10px"',echo=FALSE}
knitr::include_graphics(system.file("help/figures/hyper2.png", package = "hyper2"))
```

To cite the `hyper2` package in publications, please use @hankin2017a.
The [modern
pentathlon](https://en.wikipedia.org/wiki/Modern_pentathlon) is an
Olympic sport that comprises five different events: fencing, swimming,
horse riding, and running.  This short document discusses a dataset
taken from the [2004 Summer
Olympics](https://en.wikipedia.org/wiki/Modern_pentathlon_at_the_2004_Summer_Olympics),
analysing the order statistic for the top seven competitors:

### 2023-10-31 inst/pudding.Rmd
consistentification

---
title: "Analysis of pudding following Davidson 1970"
output: bookdown::html_document2
---

@@

<p style="text-align: right;">
![](`r system.file("help/figures/hyper2.png", package = "hyper2")`){width=10%}
</p>

This short document creates the `pudding` suite of R objects and
presents some preliminary analysis.  It is not particularly
well-structured or terse and is essentially a sequence of notes.  It
follows Davidson 1970 and the `PlackettLuce` package.

@@

# References

### Package dataset

>>>>

---
title: "Analysis of pudding following Davidson 1970"
author: "R. K. S. Hankin"
output: bookdown::html_document2
bibliography: jss_hyper3.bib
---

@@

```{r out.width='20%', out.extra='style="float:right; padding:10px"',echo=FALSE}
knitr::include_graphics(system.file("help/figures/hyper2.png", package = "hyper2"))
```

To cite the `hyper2` package in publications, please use @hankin2017a.
This short document creates the `pudding` suite of R objects and
presents some preliminary analysis.  It is not particularly
well-structured or terse and is essentially a sequence of notes.  It
follows Davidson 1970 and the `PlackettLuce` package.

@@

### Package dataset {-}
